\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fontspec}
\setmainfont{Cambria}

\begin{document}

\section*{\textbf{Terrence Zhang}}
\href{https://www.linkedin.com/in/terrence-zhang/}{LinkedIn Profile: \href{https://www.linkedin.com/in/terrence-zhang/}{linkedin.com/in/terrence-zhang/}}

\section*{\textbf{Contact Information:}}
Email: terrencezhang18@gmail.com

\section*{\textbf{Summary:}}
Highly motivated and detail-oriented performance engineer with experience in GPU hardware validation, machine learning framework internals, and large-scale systems optimization. Proven track record of solving complex problems and improving system performance.

\section*{\textbf{Technical Skills:}}

- \emph{GPU Programming}: Proficient in CUDA and OpenCL programming languages.
- \emph{Machine Learning Frameworks}: Experienced with TensorFlow and PyTorch.
- \emph{Large-Scale Systems Optimization}: Skilled in optimizing system performance using various techniques such as parallel processing, caching, and memory management.

\section*{\textbf{Professional Experience:}}

- \emph{Performance Engineer}, XYZ Corporation (2020-Present)
  - Optimized GPU hardware for improved performance and power efficiency.
  - Developed and maintained machine learning frameworks to accelerate model training and inference.
  - Collaborated with cross-functional teams to identify and resolve system bottlenecks.

- \emph{Research Assistant}, ABC University (2018-2020)
  - Assisted in the development of a novel GPU-based machine learning framework.
  - Conducted research on large-scale systems optimization techniques for improved performance and power efficiency.
  - Presented research findings at international conferences and workshops.

\section*{\textbf{Education:}}

- \emph{Bachelor's Degree}, Computer Science, ABC University (2018)

\section*{\textbf{Publications:}}
Zhang, T., et al. "A Novel GPU-Based Machine Learning Framework." Journal of Parallel and Distributed Computing, vol. 123, 2020, pp. 1-12.

\section*{\textbf{Personal Projects:}}

- \emph{GPU-Based Machine Learning Framework}: Developed a novel GPU-based machine learning framework for accelerated model training and inference.
- \emph{Large-Scale Systems Optimization Tool}: Created a tool to optimize system performance using various techniques such as parallel processing, caching, and memory management.

\end{document}